A Data-Driven Framework for Neural Field Modeling

### 2011-01-18 ltx/first_order_framework/response_to_reviews.tex

    \begin{enumerate}
        \item Do not use real data for the validation of their approach

	\emph{The authors appreciate that the only way to truly validate the proposed framework is with real data. However, before validating the method on real data we believe that it is essential to first validate the estimation method using accepted models and synthetic data, where the true and estimated parameters can be compared. In an effort to make the method employed in the paper more explicit, we have added ``To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters'' to the introduction. We plan to validate the framework on real data in future work. We have added that validating the framework on real data is required in the Conclusion.}

        \item Assume that a few kernel basis functions accurately represent the actual connectivity kernel, which might not be the case when using real data;

	\emph{Most examples presented in the paper use the Mexican hat connectivity kernel. The framework is also valid for other connectivity kernels provided they are spatially homogeneous and that they can be approximated by a set of weighted isotropic basis functions. The mathematical formulation does not place any further restrictions on the form of the spatial mixing kernel. However, more complex shapes may require more basis functions, leading to more parameters. We have added statements to the methods section (after equation~17) to be more explicit in describing subtleties of the method.}

@@

    \begin{enumerate}
        \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the reconstructed kernels seem satisfying.

		\emph{We have added to the results section describing experiment II: `These results indicate that the solution to the system may not be unique in non-ideal, practical situations. Nevertheless, the net shape of the connectivity kernel can be determined reasonably accurately.'}

        \item The use of Euler discretisation and how this affects the system's behavior.

		\emph{We have added some comments to  Appendix A, where the discretization is performed.}

@@

    \end{enumerate}

    \section{Reviewer 2}

\begin{enumerate}
    \item The handling of the (to borrow a term from numerical weather forecasting) `sub-grid scale physics' is inadequate for nervous systems (see, e.g., equation 8 (now equation 12) [The nonlinear IntegroDifference Equation]). I do very much appreciate the spectral estimation of spatial and temporal scales. But the model errors are lumped into an iid model error term that is not realistic. For instance, the flow of potassium in the extracellular spaces has a known dynamic that will affect network excitability, generating important sub-grid dynamics that is anything but iid. See, for instance, the example in Ullah et al PLoS Comp Biol 2010 where without such dynamics, state tracking and parameter estimation for a neural system fails. A beautiful overview of sub-grid effects in data assimilation is found in Kalnay's 2003 book. I would very much value the authors comments on these issues. I guess were I to respond to this question, that I might consider extending the model error term to an autoregressive model. But I will let the authors answer this question.

	\emph{A more sophisticated model for the error will provide a more realistic description of the cortical dynamics. However, this will increase the number of parameters making the estimation problem more difficult. Furthermore, the authors believe that is a benefit staying as close as possible to the classic WC equations, so future results can be compared to theoretical studies. A preferable alternative to an AR error term is to allow for time-varying parameters to account for changes in excitability levels. In future work, we also hope estimate the disturbance properties (spatial covariance and temporal variance). To address this point in this paper, we have added an extra paragraph to `Neural Field Model' section of the Methods, where we discuss the model mismatch and some basic modeling assumptions. We have also added to the Estimation section, stating that we are assuming the parameters are stationary of the estimation period. In addition, we have added to the discussion (Extensions section) with possible ways to relax these assumptions.}

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
edits with parham

The connectivity kernel can also be decomposed as 
\begin{equation}\label{DefKernelDecomp}
	 w\left(\mathbf{r},\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r},\mathbf{r}'\right) \boldsymbol{\theta},
\end{equation}
where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters. A graphical demonstration of the connectivity kernel decomposition and the net shape is provided in Fig.~\ref{fig:Figure1}. By exploiting the isotropy of the connectivity basis functions, they can be written as  
$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$. We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown. 
Note, that although the examples presented in this paper use the Mexican hat connectivity kernel, the framework is also valid for other connectivity kernels, provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\boldsymbol{\theta}$. The mathematical formulation does not restrict the shape of the kernel, where anisotropic arbitrary shapes can be represented. Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a compact support.

@@

{\bf Figure 13. Observation kernel experimental setup}. Photograph through a microscope of the Utah recording yy and the twisted bipolar current source.

>>>>

The connectivity kernel can also be decomposed as 
\begin{equation}\label{DefKernelDecomp}
	 w\left(\mathbf{r},\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r},\mathbf{r}'\right) \boldsymbol{\theta},
\end{equation}
where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters. A graphical demonstration of the connectivity kernel decomposition and the net shape is provided in Fig.~\ref{fig:Figure1}. By exploiting the isotropy of the connectivity basis functions, they can be written as  
$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$. We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown. 
Note, that although most examples presented in this paper use the Mexican hat connectivity kernel, the framework is also valid for other connectivity kernels, provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\boldsymbol{\theta}$. The mathematical formulation does not restrict the shape of the kernel, where anisotropic arbitrary shapes can be represented. Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a compact support.

@@

{\bf Figure 13. Observation kernel experimental setup}. Photograph through a microscope of the Utah array recording electrode and the twisted bipolar current source.
